Self Regulation Ontology Retest Data Report

### 2018-01-20 code/SRO_Report.Rmd
going over new data release

```{r, message=FALSE, warning=FALSE, include=FALSE}
source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Report_Helper_Functions.R')
```

@@

```{r warning=FALSE, message=FALSE}
workers = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/User_717570_workers.csv')
workers = workers %>% 
  group_by(Worker.ID) %>%
  mutate(Retest_worker=ifelse(sum(CURRENT.RetestWorker,CURRENT.RetestWorkerB2,CURRENT.RetestWorkerB3,CURRENT.RetestWorkerB4,CURRENT.RetestWorkerB5,na.rm=T)>0,1,0)) %>%
  ungroup()

worker_counts <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/retest_worker_counts.json')

@@

```{r warning=FALSE, message=FALSE}
disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/discovery_completion_dates.csv', header=FALSE)
val_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/validation_completion_dates.csv', header=FALSE)
test_comp_date = rbind(disc_comp_date, val_comp_date)
rm(disc_comp_date, val_comp_date)
retest_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/retest_completion_dates.csv', header=FALSE)
comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
names(comp_dates) <- c("sub_id", "retest_comp", "test_comp")
comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
comp_dates$test_comp = as.Date(comp_dates$test_comp)
comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)
```

>>>>

```{r, message=FALSE, warning=FALSE, include=FALSE}
source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Report_Helper_Functions.R')

test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-17-2018/'

retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_01-17-2018/'
```

@@

```{r warning=FALSE, message=FALSE}
workers = read.csv(paste0(retest_data_path,'Local/User_717570_workers.csv'))
workers = workers %>% 
  group_by(Worker.ID) %>%
  mutate(Retest_worker=ifelse(sum(CURRENT.RetestWorker,CURRENT.RetestWorkerB2,CURRENT.RetestWorkerB3,CURRENT.RetestWorkerB4,CURRENT.RetestWorkerB5,na.rm=T)>0,1,0)) %>%
  ungroup()

worker_counts <- fromJSON(paste0(retest_data_path,'/Local/retest_worker_counts.json'))

@@

```{r warning=FALSE, message=FALSE}
disc_comp_date = read.csv(paste0(retest_data_path,'Local/discovery_completion_dates.csv'), header=FALSE)
val_comp_date = read.csv(paste0(retest_data_path,'Local/validation_completion_dates.csv'), header=FALSE)
test_comp_date = rbind(disc_comp_date, val_comp_date)
rm(disc_comp_date, val_comp_date)
retest_comp_date = read.csv(paste0(retest_data_path,'Local/retest_completion_dates.csv'), header=FALSE)
comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
names(comp_dates) <- c("sub_id", "retest_comp", "test_comp")
comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
comp_dates$test_comp = as.Date(comp_dates$test_comp)
comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)
```
